The Ranked Nearest Neighbour Interchange space

### 2019-07-03 paper.tex
add alg:max_dist_path to computation chapter

In Section~\ref{section:geometry} we introduced the algorithm $\findpath$ for computing paths between arbitrary trees in $\rnni$.
Therefore, we can use it as approximation for distances in $\rnni$.
In this section we are providing pseudo-code for $\findpath$ (Algorithm~\ref{alg:find_path}) to provide further insights.
We implemented and tested this algorithm for trees on up to $k$ taxa, for which it gives the exact $\rnni$ distance. \todo{$k = ?$}
Furthermore, we saw in Section~\ref{section:diameter} that the maximum distance computed by $\findpath$ for an arbitrary pair of trees equals the diameter of $\rnni$.
Thus, if the distance between two trees equals the diameter, $\findpath$ computes the correct distance.

@@

@@

\begin{conjecture}
    Let $T$ and $R$ be trees on $n$ taxa.
    It is $d(T,R) = \Delta(\rnni)$ if, and only if, $R$ can be produced from $T$ by applying Algorithm~\ref{alg:max_dist_tree}.
\end{conjecture}

@@

\begin{lemma}
    Let $T$ and $R$ be trees.
    Algorithm~\ref{alg:find_path} gives a path of length $\frac{(n-1)(n-2)}{2}$ between $T$ and $R$ if, and only if, $R$ can be generated from $T$ by applying Algorithm~\ref{alg:max_dist_tree}.
\end{lemma}

>>>>

In Section~\ref{section:geometry} we introduced the algorithm $\findpath$ for computing paths between arbitrary trees in $\rnni$.
Therefore, we can use it as approximation for distances in $\rnni$.
In this section we are providing pseudo-code for $\findpath$ (Algorithm~\ref{alg:find_path}) to provide further insights.
We implemented and tested this algorithm for trees on up to $k$ taxa, for which it gives the exact $\rnni$ distance. \todo{$k = ?$}

@@

Recall that the Section~\ref{section:diameter} revealed that the maximum distance computed by $\findpath$ for an arbitrary pair of trees equals the diameter of $\rnni$.
Thus, if the distance between two trees equals the diameter, $\findpath$ computes the correct distance.
Note that central for proving the convexity of the set of caterpillar trees in Section~\ref{section:caterpillar_convex} was Lemma~\ref{lemma:caterpillar_dist=diameter}.
We therefore aim to find a property for any pair of trees, not only caterpillar trees, with maximum distance $\Delta(\rnni) = \frac{(n-1)(n-2)}{2}$.
Following algorithm $\findpath$, we claim following conjecture:

\begin{conjecture}
    Let $T$ and $R$ be two trees.
    It is $d(T,R) = \frac{(n-1)(n-2)}{2}$ if, and only if, $\findpath(T,R)$ computes a path of this length between $T$ and $R$.
    \label{conjecture:findpath_maxdist_correct}
\end{conjecture}

Provided Conjecture~\ref{conjecture:findpath_maxdist_correct} holds, there is a simple algorithm for computing a tree $R$ with maximum distance from any given tree $T$.
%TODO
%Explain this algorithm, not only Pseudo-Code!

\begin{lemma}
    Let $T$ and $R$ be trees.
    Algorithm~\ref{alg:find_path} ($\findpath$) gives a path of length $\frac{(n-1)(n-2)}{2}$ between $T$ and $R$ if, and only if, $R$ can be generated from $T$ by applying Algorithm~\ref{alg:max_dist_tree}.
    \label{lemma:max_dist_lemmas_equivalence}
\end{lemma}

According to Lemma~\ref{lemma:max_dist_lemmas_equivalence}, Conjecture~\ref{conjecture:findpath_maxdist_correct} is equivalence to the conjecture that two trees have maximum distance if, and only if, one can be obtained from the other by applying Algorithm~\ref{alg:max_dist_tree}.

%TODO
%proof (short explanation)

If Conjecture~\ref{conjecture:findpath_maxdist_correct} is correct, it directly would follow that the radius of $\rnni$ is $rad(\rnni) = \Delta(\rnni) = \frac{(n-1)(n-2)}{2}$, where $rad(G) = \min\limits_u \max\limits_v d(u,v)$ for graph $G$ and nodes $u$ and $v$ in $G$.

@@

@@
